Verified Time Balancing of Security Protocols \\ \large A Case Study

### 2018-12-20 Src/paper.tex
Some work towards describing a simplified protocol

  \section{The Message Preamble}

@@

  \subsection*{Alice says Hello to Bob}

@@

  \subsection*{Bob receives Alice's Hello}

@@

  \subsection*{Bob acknowledges Alice's hello via HelloAck}

@@

  \subsection*{Alice receives Bob's HelloAck}

@@

  \subsection*{Bob says Hello to Alice}

@@

  \subsection*{Alice receives Bob's Hello}

@@

  \subsection*{Alice acknowledges Bob's Hello via HelloAck}

@@

  \subsection*{Bob receives Alice's HelloAck}

@@

  \section*{The Commit Message}

@@

  \subsection*{Bob prepares a DH Part 2 Message}

@@

  \subsection*{Bob sends a Commit to Alice}

@@

  \subsection*{Alice receives Bob's Commit}

@@

  \section*{The DH Part 1 Message}

@@

  \subsection*{Alice sends DH Part 1 to Bob}

@@

  \subsection*{Bob receives Alice's DH Part 1}

@@

  \subsection*{Bob checks Alice's DH Part 1 and calculates DH 

@@

  \section*{The DH Part 2 Message}

@@

  \subsection{Bob sends DH Part 2 to Alice}

@@

  \subsection*{Alice checks Bob's DH Part 2 and calculates DH 

@@

>>>>

  \section{A description of the ZRTP Protocol up to public key 
           exposure.}
  \subsection{The Message Preamble}

@@

  \subsubsection{Alice says Hello to Bob}

@@

  \subsubsection{Bob receives Alice's Hello}

@@

  \subsubsection{Bob acknowledges Alice's hello via HelloAck}

@@

  \subsubsection{Alice receives Bob's HelloAck}

@@

  \subsubsection{Bob says Hello to Alice}

@@

  \subsubsection{Alice receives Bob's Hello}

@@

  \subsubsection{Alice acknowledges Bob's Hello via HelloAck}

@@

  \subsubsection{Bob receives Alice's HelloAck}

@@

  \subsection{The Commit Message}

@@

  \subsubsection{Bob prepares a DH Part 2 Message}

@@

  \subsubsection{Bob sends a Commit to Alice}

@@

  \subsubsection{Alice receives Bob's Commit}

@@

  \subsection{The DH Part 1 Message}

@@

  \subsubsection{Alice sends DH Part 1 to Bob}

@@

  \subsubsection{Bob receives Alice's DH Part 1}

@@

  \subsubsection{Bob checks Alice's DH Part 1 and calculates DH 

@@

  \subsection{The DH Part 2 Message}

@@

  \subsubsection{Bob sends DH Part 2 to Alice}

@@

  \subsubsection{Alice checks Bob's DH Part 2 and calculates DH 

@@

  \section{A Simplification of ZRTP}
  \subsection{Negotiated Protocols}
  To simplify the formal verification of timing observability, 
  this simplified protocol will forgo the agreement process between
  the parties and all parties will assume the following:
    \item Let $ha$ represent the agreed-upon hash algorithm 
          SHA-256.
    \item Let $ca$ represent the agreed-upon cipher algorithm 
          AES-1.
    \item Let $at$ represent the agreed-upon auth tag type
          HS32 - based on HMAC-SHA1 in RFC 3711.
    \item Let $kt$ represent the agreed-upon key agreement
          type DH2k, p=2048 Bit Prime as per RFC 3526.
    \item Let $st$ represent the agreed-upon short authentication
          string type B32
  \subsubsection{The Hello and HelloAck Messages}
  If this protocol assumes pre-agreement on protocol parameters
  by Alice and Bob, and assumes that both Alice and Bob pre-compute
  $h0$, $h1$, $h2$, and $h3$ then the ``Hello'' messages and the 
  corresponding ``HelloAck'' messages can be considered to have
  a constant time, and thus possibly be ommited for the purpose of
  verifying timing observability.
